
---
title: "Escoviopsis vesicle morphometrics"
graphics: yes
date: '`r Sys.Date()`'
output:
  pdf_document:
    toc: yes
fontsize: 12pt
---

\pagebreak

```{r, echo=T, message=FALSE, warning=FALSE}
library(knitr)
library(dplyr)
library(Momocs)
library(magick)
library(reshape2)
```

# Dibujos de la publicación

```{r, fig.height=4, fig.width=7, fig.align='center',echo=T, cache=F, message=FALSE, warning=FALSE}
image_read("Escovopsis_Microscopic-structures.jpg") %>% 
  as.raster() %>% 
  plot()
```

# Siluetas hechas de los dibujos

```{r, fig.height=4, fig.width=7, fig.align='center',echo=T, cache=F, message=FALSE, warning=FALSE}
image_read("Escovopsis_Microscopic-structures_outlines.jpg") %>% 
  as.raster() %>% 
  plot()
```

\pagebreak 

Importamos las siluetas cortadas

```{r, label="import vesicles", echo=T, cache=T, message=FALSE, warning=FALSE,results='hide'}
# Importamos las siluetas como coordenadas
jpg.list <- list.files("outlines",pattern = ".jpg")
coords <- import_jpg(jpg.paths=paste0("outlines","/", jpg.list),
                     auto.notcentered = T) 
outlines <- Out(coords) 

# Les limpiamos el nombre
names_outlines <- names(outlines) %>% data.frame() %>% setNames("image")
names_outlines <- colsplit(names_outlines$image,pattern="_",
                           names=c("letter","shape"))

# Y les asignamos el nombre limpio 
names(outlines) <- names_outlines$shape

# Y la letra y nombre limpio en el campo de los grupos para facilitar los gráficos
outlines$fac <- names_outlines
```

# Los especímenes dentro de R

```{r, fig.height=4.5, fig.width=4.5, fig.align='center', echo=T, cache=FALSE, message=FALSE, warning=FALSE}
panel(outlines, names = "shape")
```

\pagebreak

Here we do the elliptic Fourier analysis, PCA of the results and look at the percent explained by each Principal Component

```{r, label="elliptic Fourier analysis", echo=T, cache=FALSE, message=FALSE, warning=FALSE}
efou_outlines <- efourier(outlines, norm=F, nb.h=32, smooth.it=1) 
efou_outlines <- rm_sym(efou_outlines)
pca_outlines <- PCA(efou_outlines)

pc_contribution <- pca_outlines %>% summary()
pc_contribution$importance[,1:3] %>% kable(caption = "PC contribution")
```

Graphical representation of variation explained in each of the first three PC

```{r, fig.height=4, fig.width=6, fig.align='center',echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
PCcontrib(pca_outlines, nax=c(1:3), sd.r = c(-1.5, -1, 0, 1, 1.5))
```

\pagebreak

# Morfoespacio

```{r,fig.height=5, fig.width=7, fig.align='center', echo=T, cache=FALSE, message=FALSE, warning=FALSE}
plot_PCA(pca_outlines, morphospace=F, points=F,chull=F,eigen=F,
         zoom=0.85, center_origin = F,legend=F) %>%
  layer_labelpoints() %>%
  layer_points(cex=1, transp=0.25) %>% 
  layer_box(border="black",lwd=2) %>%
  layer_axesvar() %>% 
  layer_morphospace_PCA(size=1, nr = 5, nc = 3, pos="range") %>% 
  layer_title("Morphospace of PC1-PC2 with theoretical 
              morphospace in the background")
```

\pagebreak

```{r,fig.height=5, fig.width=7, fig.align='center', echo=T, cache=FALSE, message=FALSE, warning=FALSE}
plot_PCA(pca_outlines, morphospace=F, points=F,chull=F,eigen=F,
         zoom=0.85, center_origin = F,legend=F) %>%
  layer_labelpoints() %>%
  layer_box(border="black",lwd=2) %>%
  layer_axesvar() %>% 
  layer_morphospace_PCA(size=1, nr = 5, nc = 3, pos="xy") %>% 
  layer_title("Morphospace of PC1-PC2 with illustration of 
  each specimen based on these two axes")
```
